testibng

### 2024-01-07 Code/R FIle.qmd
fxed qmd
cleaned data

```{r}
library(tidytuesdayR)
library(tidyverse)
```

@@

# Wage Data
tuesdata <- tidytuesdayR::tt_load(2021, week = 7)

income_distribution <- tuesdata$income_distribution

# Minimum Wage Data
minimum_wage <- read_csv("../Data/minimum_wage_data.csv")

rm(tuesdata)
```

@@

```{r}
head(demographics)
head(wages)
head(states)
head(house)
```

@@

```{r}
house <- house |>
  mutate(state = str_to_sentence(state)) |>  # change from all caps to sentence case
  mutate(regions = state.region[match(state_po, state.abb)]) # add regions 
```

@@

>>>>

```{r}
library(tidyverse)
```

@@

# Wage Data
income_distribution <- read_rds("../Data/income_distribution.rds")

# Minimum Wage Data
minimum_wage <- read_csv("../Data/minimum_wage_data.csv")
```

@@

```{r}
head(union_demographics)
head(union_wages)
head(union_states)
head(house)
head(income_distribution)
head(minimum_wage)
```

@@

```{r}
house <- house |>
  mutate(state = str_to_sentence(state)) |> # change from all caps to sentence case) 
  select(!(state_fips:office)) |> #Remove unwanted columns
  select(!(stage:candidate)) |> 
  select(!(writein:fusion_ticket))
```

```{r}
union_demographics <- union_demographics |> 
  select(-sample_size) |> 
  mutate(union_type = facet, .keep = "unused")
```

```{r}
union_wages <- union_wages |> 
  select(-sample_size,
         -at_cap) |> 
  mutate(percent_difference = union_wage_premium_raw, .keep = "unused") |> 
  mutate(percent_difference_adjusted = union_wage_premium_adjusted, .keep = "unused") |> 
  mutate(union_type = facet, .keep = "unused")
```

```{r}
union_states <- union_states |> 
  select(-state_census_code,
         -observations)
```

```{r}
income_distribution <- income_distribution |> 
  select(-number) |> 
  select(!ends_with("moe")) |> 
  select(year:income_mean) |> 
  distinct(year, race, income_median, income_mean, .keep_all = TRUE) 
```

```{r}
minimum_wage <- minimum_wage |> 
  select(Year:CPI.Average)
```

@@

```{r}
test <- minimum_wage
```
